Proof Reconstruction with Athena\\(Work in Progress)

### 2017-04-19 slides/athenatalk.tex
[ slides ] tstp, tptp explanation.

\begin{frame}{Keywords}
  \begin{block}{Proof Assistant}
  is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\footnote{Matita development team, Matita website, http://matita.cs.unibo.it/index.shtml}
  \end{block}
  \begin{block}{ATP}
  An \text{A}utomatic \textbf{T}heorem \textbf{P}rover is software program 
  \end{block}
\end{frame}

@@

%% \begin{frame}{Agda}
%%   A proof verified of the previous derivation output by Athena.
%% {\footnotesize
%%   \problemtptp[basic-4.agda]{../test/prop-pack/problems/basic/basic-4.agda}{0}
%% }
%% \end{frame}

% The tool : Athena.
% Its components:
% - agda-prop (logic framework)
% - agda-metis (ATP rules)
% - prop-pack (problems)

>>>>

\begin{frame}{Keywords}
  \begin{block}{Proof Assistant}
    is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\\
    - Agda, Isabelle/HOL, HOL Light, Coq.
  \end{block}
  \begin{block}{\text{A}utomatic \textbf{T}heorem \textbf{P}rover}
    Is software program that tries to prove conjecture based on a list of hypothesis.\\
    - Metis, Z3, Vampire, EProver, iProver, SPSS.
  \end{block}
\end{frame}

@@

\begin{frame}{Agda}
   A verified proof of the previous derivation output by Athena.

  \begin{figure}
    \includegraphics[scale=0.35]{basic-4}
    \label{im:basic}
    \caption{Type-checked Proof.}
  \end{figure}

\begin{frame}{Natural deduction tree}
  $\Gamma , p \vdash p$
\begin{proof}\hfill
\label{basic-der}
\begin{prooftree}
\AxiomC{$\Gamma \vdash a_1$}
\RightLabel{\scriptsize({\bfseries weaken $\neg\ \text{subgoal}_0$})}
\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash a_1$}
\RightLabel{\scriptsize({\bfseries canonicalize})}
\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash p$}
\AxiomC{$\Gamma \vdash p$}
\RightLabel{\scriptsize({\bfseries assume})}
\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
\RightLabel{\scriptsize({\bfseries canonicalize})}
\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
\RightLabel{\scriptsize({\bfseries simplify})}
\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
\BinaryInfC{$\bot$}
\RightLabel{\scriptsize({\bfseries RAA})}
\UnaryInfC{$\Gamma \vdash p$}
\end{prooftree}
% A tree deduction of problem \ref{prob1}
\end{proof}
\end{frame}
% The tool : Athena.
% Its components:
% - agda-prop (logic framework)
% - agda-metis (ATP rules)
% - prop-pack (problems)
